---
title: "Data 607: Week 2 Assignment - SQL and R"
author: "C. Rosemond 090819"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load RPostgres and DBI packages

I load the RPostgres and DBI packages to enable connection to a local PostgreSQL database.

```{r load}
library(RPostgres)
library(DBI)
```

## Connect to database and check connection

I set my password then connect to a local PostgreSQL database. I then check the connection by listing the tables within the database.

```{r connect}
pw <- ''
connect <- dbConnect(RPostgres::Postgres(),
                 dbname = 'data607fall19',
                 host = 'localhost',
                 port = 5432,
                 user = 'postgres',
                 password = pw)
rm(pw)
dbListTables(connect)
```

## Read in table with movie ratings by critic

I read in the ratings table, which contains movie ratings from 10 critics, and assign it to an object, also called ratings. I then check the object.

Movies ("column", Title):
  "endgame", Avengers: Endgame
  "midsommar", Midsommar
  "lion_king", The Lion King
  "john_wick3", John Wick: Chapter 3 - Parabellum
  "last_sf", The Last Black Man in San Francisco
  "once_hollywood", Once Upon a Time in Hollywood

```{r read}
ratings <- dbReadTable(connect, "ratings")
str(ratings)
ratings
```
