---
title: "Data 607 - Week 2 Lab"
author: "C. Rosemond 090219"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load requisite packages

I load the RPostgres and DBI packages.

```{r load}
library(RPostgres)
library(DBI)
```

## Connect to database and check connection

I set my password then connect to a local PostgreSQL database. I then check the connection by listing the tables within the database.

```{r connect}
pw <- ''
connect <- dbConnect(RPostgres::Postgres(),
                 dbname = 'data607fall19',
                 host = 'localhost',
                 port = 5432,
                 user = 'postgres',
                 password = pw)
rm(pw)
dbListTables(connect)
```

## Read in table with tuberculosis rates by country by year

I read in the tb_rate table, which contains tuberculosis rates by country by year, and assign it to an object, also called tb_rate. The rates are in percentage points, e.g., in 1997, Afghanistan had a tuberculosis rate of 0.001 percent. I then check the first and last six rows.

```{r read}
tb_rate <- dbReadTable(connect, "tb_rate")
str(tb_rate)
head(tb_rate)
tail(tb_rate)
```
